### 2021-11-13 NSF2021/Description/specificaim1.tex
finished up first pass through SA1

\begin{wrapfigure}[10]{r}{0.65\textwidth}
  \vspace{-22pt}
  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPA.pdf}
  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPB.pdf}
  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPC.pdf}  
\caption{\label{fig:bcs} Boundary conditions characterize the type of
  water structure: an amphiphilic particle (left), a hydrophobic
  particle with anisotropic intensity (middle), a water structure with
  plus/minus polarity (right). The dashed curve is the boundary of the
  disk and the arrow its director.}
\end{wrapfigure}
The coupling between the Stokes equations \eqref{eq:stokes} and the
semilinear elliptic equation \eqref{eq:SL} comes from the first
variation of the energy functional. The particles minimize the free
energy $F[u]$ by altering the location of hydrophobic interfaces. It is
possible to calculate the rate of change of $F[u]$ using variation of
the domain~\cite{Bandle2015, Schiffer1954, Grinfeld2010}. Carrying out
this variation yields a 
%The hydrophobic forces are torques are
%\begin{equation}
%  \label{eq:hydrophobicAttraction}
%  \FF_i^{\text{hydro}} = \int_{\Gamma_i} {\bf T}\cdot \nnu \, \dif s, 
%    \quad 
%    T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot
%    ({\bf T} \cdot \nnu) \dif s.
%\end{equation}
surface force density 
\begin{align}
  \label{eq:stress}
\mathbf{T}
= C \left[ \rho^{-1} f(u) \mathbf{I}
  + \rho \left(|\nabla u|^2 \mathbf{I} - \nabla u \nabla u^T\right)\right].
\end{align}
The imposed forces and torques from the integration of $\mathbf{T}$
along the particle boundary. The density~\eqref{eq:stress} was first
introduced by~\cite{Fu2018_SIAM} and is the higher-dimensional analogue
of disjoining pressure calculated by \cite{MaRa76, ErLjCl89, KoNa15,
Nagle17, KUZMIN2005}. It is the mathematical ingredient responsible for
forming particle aggregates that sequester their hydrophobic surface
regions.

@@

\subsubsection{Janus-particle self-assembly} 
When $f(u) = u^2$, and the water structure has its lowest potential
value at $u=0$ which represents bulk water. The solutions of
\eqref{eq:SL} have a boundary layer structure and decay to $0$ in the
bulk with the decay length $\rho$. Even in this linear response case, a
number of morphologies arise by altering boundary conditions.

@@

In summary, the hydrophibic interaction-mobility problem model yields
rich morphologies that are valuable in the synthesizing multiphasic and
anisotropic colloids \cite{Bradley2016,Mallory2017,Bradley2017}.
The main experimental challenges include the ability to
decouple particle surface properties.
The goal is to obtain numerically aided 
syntheses and assembly of soft matter materials.
Applications in this area include cargo-carrying capacity, 
catalytic activity, or stimuli-responsive shape-change to amplify colloid
utility for a wide range of  spanning environmental remediation to drug
delivery \cite{McBr21, HaBr20}.

%\begin{wrapfigure}[14]{l}{0.5\textwidth}
%\includegraphics[width=0.5\textwidth]{figures/SpecificAi%m1/multilamelar.pdf}
%\caption{\label{fig:multilamelar}
%  Experimentalists can transform unilamellar vesicles to% multilamellar
%  vesicles by altering the quality of the solvent
%    \cite{deMeetal21}.
%  In \eqref{eq:SL}, the solvent quality enters through t%he potential
%  $f(u)$ and boundary conditions. 
%}
%\end{wrapfigure}
The main modeling challenge is to translate the phenomenological
parameters, e.g. boundary conditions, into measurable quantities
such as contact angles. Collaboration with experimental groups will
use numerical methods to predict parameter regimes 
to control particle-particle interactions. In Specific Aim 3, we
discuss how to include ions and surface charge.

@@

Here, the order parameter $u$ is the mean number of nearest neighbors
per water molecule. The value $u_0 = 4$ gives a local minimum for the
ideal tetrahadral water network found at hydrophobic surfaces. The value
$u_1 \sim 4.4$ gives the absolute minimum in the bulk where there is a
mixture of four and five-coordinated waters. When particles are
well-separated, the energetic cost for filling the interstitial region
with $u_0$-phase water is prohibitive and there is a phase shift from
the $u_0$ to $u_1$ water order---the attraction landscape is more or
less identical to the linear response theory. Conversely, when particles
are proximal, it becomes energetically favorable to coalesce
$u_0$-phases. This introduces a line tension for the phase transition.

Equation~\eqref{eq:SL} takes the form of a steady-state Allen-Cahn
equation. The Allen-Cahn equation is used in phase field formulations of
immisible fluids, for example. PI RR and colaborators launched the
simulation and asymptotic analysis of phase field functionals of
membrane elastic energy, devising functionals for for the squared mean
curvature (Willmore) energy~\cite{0951-7715-18-3-016}, spontaneous
curvature~\cite{Du05} and Gaussian curvature energy~\cite{DuEuler}, as
well as energetic variational approaches to coupling membrane elasticity
to fluids~\cite{QiangDu09}.

One potential application of the Allen-Cahn-type formulation is to
explaning measured hydrophobic attraction profiles.
The experimental data on hydrophobic attraction between 
is well-established and the literature contains data for a number of
solvents and hydrocarbon species. The experimental measurements
are well-fit by a double exponential curve in the 10 to 100 nanometer range
of separation. Below 10~nm, however, there is an amplification of force
and the attraction follows a much steeper force law not accounted
for by past phenomenoloical theories~\cite{Lin2005}.

It may be the case that the double-well formulation recreates the long
and short-range interactions. The advantage is that the two-dimensional
simulations can replicate the experimental setup better than prior,
one-dimensional theoretical work Some of the model parameters directly
connect to long-range decay lengths and energy cost of creating
hydrophobic-water interfaces with established ranges of values. Other
parameters, like the well structure, are fit to the measured data. These
base-line simulations will allow us to move on to provide more accurate
colloidal suspension simulations.

Other approaches will be required if the modified phenomenological
theory does not recreate the measured force curves. We can rule out
convection in the water structure since the time scale of particle
motion is much larger than the hydrogen-bond lifetimes. One approach is
to consider Gaussian fluctuation. Here, we expand the free energy
functional around the saddle point solution. The fluctuation energy
then involves calculation of the eigenfunctions of the second variation
of the free energy. This accounts for the fact that experimental
measurements are carried out at finite temperatures, where thermal
fluctuations should ideally also be considered.

>>>>

\begin{wrapfigure}[10]{r}{0.65\textwidth}
  \vspace{-22pt}
  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPA.pdf}
  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPB.pdf}
  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPC.pdf}  
\caption{\label{fig:bcs} Boundary conditions characterize the type of
  water structure: an amphiphilic particle (left), a hydrophobic
  particle with anisotropic intensity (middle), a water structure with
  plus/minus polarity (right). The dashed curve is the boundary of the
  disk and the arrow its director.}
\end{wrapfigure}
The coupling between the Stokes equations~\eqref{eq:stokes} and the
semilinear elliptic equation~\eqref{eq:SL} comes from the first
variation of the energy functional. The particles minimize the free
energy $F[u]$ by altering the location of hydrophobic interfaces. It is
possible to calculate the rate of change of $F[u]$ using variation of
the domain~\cite{Bandle2015, Schiffer1954, Grinfeld2010}. Carrying out
this variation yields a 
%The hydrophobic forces are torques are
%\begin{equation}
%  \label{eq:hydrophobicAttraction}
%  \FF_i^{\text{hydro}} = \int_{\Gamma_i} {\bf T}\cdot \nnu \, \dif s, 
%    \quad 
%    T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot
%    ({\bf T} \cdot \nnu) \dif s.
%\end{equation}
surface force density 
\begin{align}
  \label{eq:stress}
\mathbf{T}
= C \left[ \rho^{-1} f(u) \mathbf{I}
  + \rho \left(|\nabla u|^2 \mathbf{I} - \nabla u \nabla u^T\right)\right].
\end{align}
The imposed forces and torques from the integration of $\mathbf{T}$
along the particle boundary. The density~\eqref{eq:stress} was first
introduced by~\cite{Fu2018_SIAM} and is the higher-dimensional analogue
of disjoining pressure calculated by \cite{MaRa76, ErLjCl89, KoNa15,
Nagle17, KUZMIN2005}. It is the mathematical ingredient responsible for
forming particle aggregates that sequester their hydrophobic surface
regions.

@@

\subsubsection{Janus-particle self-assembly} 
When $f(u) = u^2$, and the water structure has its lowest potential
value at $u=0$ which represents bulk water. The solutions
of~\eqref{eq:SL} have a boundary layer structure and decay to $0$ in the
bulk with the decay length $\rho$. Even in this linear response case, a
number of morphologies arise by altering boundary conditions.

@@

In summary, the hydrophibic interaction-mobility problem model yields
rich morphologies that are valuable in the synthesizing multiphasic and
anisotropic colloids~\cite{Bradley2016,Mallory2017,Bradley2017}. The
main experimental challenges include the ability to decouple particle
surface properties. The goal is to obtain numerically aided syntheses
and assembly of soft matter materials. Applications in this area include
cargo-carrying capacity, catalytic activity, or stimuli-responsive
shape-change to amplify colloid utility for a wide range of spanning
environmental remediation to drug delivery~\cite{McBr21, HaBr20}.

%\begin{wrapfigure}[14]{l}{0.5\textwidth}
%\includegraphics[width=0.5\textwidth]{figures/SpecificAi%m1/multilamelar.pdf}
%\caption{\label{fig:multilamelar}
%  Experimentalists can transform unilamellar vesicles to% multilamellar
%  vesicles by altering the quality of the solvent
%    \cite{deMeetal21}.
%  In \eqref{eq:SL}, the solvent quality enters through t%he potential
%  $f(u)$ and boundary conditions. 
%}
%\end{wrapfigure}
The main modeling challenge is to translate the phenomenological
parameters, e.g.~boundary conditions, into measurable quantities such as
contact angles. Collaboration with experimental groups will use
numerical methods to predict parameter regimes to control
particle-particle interactions. In \S~\ref{subsec:specific_aim_3}, we
discuss how to include ions and surface charge.

@@

Here, the order parameter $u$ is the mean number of nearest neighbors
per water molecule. The value $u_0 = 4$ gives a local minimum for the
ideal tetrahedral water network found at hydrophobic surfaces. The value
$u_1 \sim 4.4$ gives the absolute minimum in the bulk where there is a
mixture of four and five-coordinated waters. When particles are
well-separated, the energetic cost for filling the interstitial region
with $u_0$-phase water is prohibitive and there is a phase shift from
the $u_0$ to $u_1$ water order---the attraction landscape is more or
less identical to the linear response theory. Conversely, when particles
are proximal, it becomes energetically favorable to coalesce
$u_0$-phases. This introduces a line tension for the phase transition.

Equation~\eqref{eq:SL} takes the form of a steady-state Allen-Cahn
equation. The Allen-Cahn equation is used in phase field formulations of
immiscible fluids, for example. PI RR and collaborators launched the
simulation and asymptotic analysis of phase field functionals of
membrane elastic energy, devising functionals for for the squared mean
curvature (Willmore) energy~\cite{0951-7715-18-3-016}, spontaneous
curvature~\cite{Du05}, and Gaussian curvature energy~\cite{DuEuler}, as
well as energetic variational approaches to coupling membrane elasticity
to fluids~\cite{QiangDu09}.

One potential application of the Allen-Cahn-type formulation is to
explain measured hydrophobic attraction profiles. The experimental data
on hydrophobic attraction between \todo{between what?} is
well-established and the literature contains data for a number of
solvents and hydrocarbon species. The experimental measurements are
well-fit by a double exponential curve in the 10--100~nm range of
separation. Below 10~nm, however, there is an amplification of force and
the attraction follows a much steeper force law not accounted for by
past phenomenological theories~\cite{Lin2005}.

It may be the case that the double-well formulation recreates the long
and short-range interactions. The advantage is that the two-dimensional
simulations can replicate the experimental setup better than prior,
one-dimensional theoretical work. Some of the model parameters directly
connect to long-range decay lengths and energy cost of creating
hydrophobic-water interfaces with established ranges of values. Other
parameters, like the well structure, are fit to the measured data. These
base-line simulations will allow us to move on to provide more accurate
colloidal suspension simulations.

Other approaches will be required if the modified phenomenological
theory does not recreate the measured force curves. We can rule out
convection in the water structure since the time scale of particle
motion is much larger than the hydrogen-bond lifetimes. One approach is
to consider Gaussian fluctuations. Here, we expand the free energy
functional around the saddle point solution. The fluctuation energy then
involves calculation of the eigenfunctions of the second variation of
the free energy. This accounts for the fact that experimental
measurements are carried out at finite temperatures, where thermal
fluctuations should ideally also be considered.
